### 2013-09-15 chi2014/introduction.tex
more writing

This format is to be used for submissions that are
published in the conference proceedings.  We wish to give
this volume a consistent, high-quality appearance. We
therefore ask that authors follow some simple
guidelines. In essence, you should format your paper
exactly like this document. The easiest way to do this is
simply to download a template from the conference web
site, and replace the content with your own material.

>>>>

Whether in research or industry, productivity can be hamstrung by the need to generate creative or novel ideas. Given the ubiquity of idea generation tasks, it is desireable to provide generalizable automated methods of solving them. Automated computational methods to solve specific problems are unlikely to appear without significant advances in natural language processing and artificial intelligence. As a result, we are left with human-centric solutions, such as brainstorming.

Brainstorming is a tool proposed by Osborne [CITE] that has achieved widespread popularity and similarly widespread research and controversy. Brainstorming methods have been applied in many scenarios, from spatially co-located participants to electronic brainstorming over computer networks [CITE]. The introduction of crowd marketplaces such as Amazon's Mechanical Turk [CITE] and the corresponding paradigm of massively parallel Human Intelligence Tasks provide both a natural venue to solicit ideas and a new context in which to establish models of brainstorming activity.

This setting introduces unique challenges. For example, crowd marketplaces are driven by financial transactions, while participants in traditional brainstorming settings are required and motivated to generate ideas for a given duration. Guidelines and points of comparison are needed.

In the course of their research in Human-Computer Interactions, two of the authors went looking for these sets of guidelines to apply them to a crowd idea generation task. While previous work has utilized brainstorming techniques in crowd marketplaces [CITE], we were unable to find any generalizable models or guidelines for brainstorming in the context of the crowd. Models such as Nijstaf and Stroebe's SIAM [CITE] make and test predictions regarding in-person brainstorming, but we did not find similar baselines for electronic or crowd brainstorming.

This paper and corresponding data set provide a baseline for the idea generation process in crowd marketplaces. We establish a corpus of brainstorming data in a restricted design space with two axes: idea generation problem, and number of responses requested of a single crowd worker.

We provide a method for clustering responses to idea generation problems and provide a detailed description of the resulting data set, which has been made publically available. We demonstrate the saturation of ideas received over time, and show that the rate of saturation, and size of the saturated idea set, originality of ideas and generality of ideas vary between conditions.

Furthermore, we examine predictions made by Nijstaf and Stroebe's model of in-person brainstorming and test them in the context of crowd brainstorming. We find that the tested predictions hold: that ideas generated in sequence tend to belong to the same category, and that the time spent to generate when changing categories is signficantly greater than when generating ideas within the same category.

Finally, we briefly outline qualitative findings in the data, and recommend future work motivated by these findings.

### 2013-09-15 chi2014/method.tex
more writing

We began the process of soliciting responses to brainstorming tasks in a crowd marketplace. Throughout the experimental process, particular aspects of the experimental design remained fixed.

@@

Upon accepting a HIT, participants are randomly assigned into a \emph{brainstorming problem} condition. We ensured that participants completing multiple HITs are not exposed to the same brainstorming task twice.

@@

\subsubsection{Data Collection}

@@

In examining the data, we found responses advocating a specific problem-solving strategy would nonetheless vary in generality. We introduce terminology here that will allow us to better describe and formalize these differences.

@@

One researcher coded the data to produce the idea forests described above. The clustering algorithm is described in Figure FIG. Instances are added one at a time to the existing idea forest. In brief summary, the root idea that most closely matches the strategy in the instance is selected, and then that root idea and the new instance are compared in generality. This process may be repeated depending on this generality relationship, until instance is either placed in an existing idea or a new idea node is created.

@@

\begin{figure*}[h]
\begin{verbatim}
for each instance:
  idea_node = new node including instance
  current_node = root of forest
  do:
    best_match = max_similarity(idea_node, current_node.children)

>>>>

\section{Method}

In order to develop an adequate model of baseline brainstorming performance in crowd marketplaces, it was necessary to establish a corpus of data. Over the course of four months we repeatedly collected responses to brainstorming tasks. Throughout the experimental process, particular aspects of the experimental design remained fixed.

@@

Upon accepting a HIT, participants were randomly assigned into a \emph{brainstorming problem} condition. We ensured that participants completing multiple HITs are not exposed to the same brainstorming task twice.

@@

\subsubsection{Data Collected}

In total, 341 HITs were complteed by 280 distinct participants. A breakdown of responses across conditions is given in table TAB. In cases when a single participant answered the same question multiple times, all HITs after the first were dropped for subsequent analysis.

\begin{tabular}[h!]{r | l l l l l l }
& 5 & 10 & 20 & 50 & 75 & 100 \\ \hline \hline
HITs (MP3) & 59 & 49 & 23 & 10 & 10 & 10 \\
HITs unique (MP3) & 57 & 39 & 21 & 9 & 10 & 10 \\ \hline
HITs (Turk) & 11 & 10 & 11 & 10 & 9 & 9 \\
HITs unique (Turk) & 11 & 9 & 11 & 9 & 9 & 7 \\ \hline
HITs (Forgot) & 10 & 10 & 10 & 12 & 11 & 11 \\
HITs unique (Forgot) & 10 & 8 & 9 & 12 & 10 & 10 \\ \hline
HITs (Charity) & 9 & 10 & 10 & 8 & 10 & 9 \\
HITs unique (Charity) & 9 & 9 & 10 & 7 & 9 & 9 \\ \hline
HITs (total) \\
HITs unique (total) \\ \hline
\end{tabular}

There is significantly more data for the MP3 condition than for any of the others. Despite at least 7 unique HITs for each of the 24 problem x number conditions, we found that the limited number of total responses for the 5, 10 and 20 conditions precluded significant analysis. To that end, we selected the MP3 player problem to further expand the data set to 400 (TODO: maybe not true) responses per number condition.

@@

As we began to examine the data, it quickly began apparent that there are nuances in discussing responses to brainstorming tasks. In the interest of facilitating this discussion, we introduce terms here that will be used for the remainder of the paper.

@@

One researcher coded responses the MP3 problem to produce an idea forest as described above. The MP3 problem was chosen because it was subjectively easiest to distinguish between and categorize ideas.

The clustering algorithm is described in Figure FIG. Instances are added one at a time to the existing idea forest. In brief summary, the root idea that most closely matches the strategy in the instance is selected, and then that root idea and the new instance are compared in generality. This process may be repeated depending on this generality relationship, until instance is either placed in an existing idea or a new idea node is created.

\begin{figure*}[h!]
\small
\begin{verbatim}
for each instance:
  idea_node = new node including instance
  current_node = root of forest
  do:
    best_match = max_similarity(idea_node, current_node.children)

@@
